\Large{Implementation of Linear Spatial Filter on Video Stream Using FPGA Hardware Accelerator}

### 2021-05-30 include/article-en.tex
include
article en

\subsection{Konvolusi}

@@

The researchers used computation time, frame rate (FPS), CPU usage, memory usage, resident memory (RES), shared memory (SHR), and virtual memory usage (VIRT) to measure the performance of applying linear spatial filters with ARM and FPGA processors.

@@

\subsubsection{CPU Usage}
% Pada penelitian ini peneliti menggunakan fitur yang tersedia pada sistem operasi Linux yang berjalan di FPGA Development Board untuk melihat persentase penggunaan CPU pada proses penerapan filter spasial linear. Program ini menampilkan informasi tentang proses-proses yang berjalan pada sistem operasi seperti ID sebuah proses, user yang menjalankan proses tersebut, \textit{memory} yang digunakan, status sebuah proses, persentase CPU yang digunakan dan lainnya.

The researchers used the features available on the Linux operating system running on the FPGA Development Board to see the percentage of CPU usage in the process of applying linear spatial filters. This program displays information about processes running on the operating system such as the ID of a process, the user running the process, the memory used, the status of a process, the percentage of CPU used and others.

\subsubsection{Memory Usage}

@@

\subsection{Sistem Design}
\begin{figure}[ht]
    \includegraphics[width=1\linewidth, center]{images/rancangan-sistem2.png}
    \caption{Sistem Design.}
    \label{fig:rancangan-sistem}
\end{figure}

@@

The spatial filter process is carried out by convolution operations on each matrix with a predetermined kernel. This convolutional operation produces a new matrix with a size of 1280x720. The resulting matrix is then represented as a digital image, hereinafter referred to as the filter result. The filter result of each frame is displayed to the monitor via HDMI Output on the FPGA Development Board continuously.

@@

% 200 frame
% Data waktu komputasi menggunakan 200 frame pada maasing-masing kernel dapat dilihat pada tabel \ref{table:hasil-time200} dan grafik pada gambar \ref{fig:chart-time200}. Rata-rata waktu komputasi dengan prosesor ARM menggunakan 200 frame adalah 29,06 detik, sedangkan rata-rata waktu komputasi dengan FPGA menggunakan 200 frame hanya 3,32 detik.

@@

\subsection{CPU usage}

@@

Comparative data on CPU usage on each kernel with ARM and FPGA processors can be seen in the \ref{table:cpu-result} table and the chart in the \ref{fig:chart-cpu} table. The average CPU usage with ARM processors is 99.58\% while with FPGA it is 84.75\%. This data shows that CPU usage with ARM processors is slightly greater than with FPGAs.

\begin{atable}
    \caption{Comparison table of CPU Usage using ARM prosesor and FPGA.}
    \label{table:hasil-cpu}
    \csvreader[
        head to column names,
        tabular=lcc,
        separator=semicolon,
        before table=\rowcolors{2}{gray!15}{gray!30},
        table head= \rowcolor{gray!50!black} 
            \color{white} Filter & 
            \color{white} Prosesor ARM (\%) & 
            \color{white} FPGA (\%)\\]
        {tables/hasil-cpu.csv}
        {
            filter=\filter, 
            arm=\arm, 
            fpga=\fpga}
        {
            \filter & 
            \arm & 
            \fpga }
\end{atable}
\begin{figure}[H]
    \includegraphics[width=0.81\linewidth, center]{images/chart/chart-cpu.png}
    \caption{Comparison chart of CPU usage using ARM prosesor and FPGA.}
    \label{fig:chart-cpu}
\end{figure}

@@

The biggest CPU usage with ARM processors is the average blur kernel (99.83\%) and the FPGA on the sobel horizontal kernel (86.22\%). The CPU usage with ARM processors is the sharpening and sobel horizontal kernel (99.47\%) and with the FPGA on the gaussian blur kernel (83.70\%).

@@

To calculate the CPU usage efficiency of an FPGA compared to an ARM processor, the following equation is used:
\begin{equation*}
    % \label{eq:efisiensi}
    \begin{split}
& = 100\% - \left( \frac{CPU\ FPGA}{CPU\ ARM Prosesor} \times 100\% \right) \\
& = 100\% - \left( \frac{84.75}{99.58} \times 100\% \right) \\
& = 100\% - 85.11\% \\
& = 14.89\% \\
    \end{split}
\end{equation*}
% sehingga diperoleh efisiensi penggunaan CPU FPGA dibandingkan dengan prosesor ARM adalah sebesar 14.89\%.

the efficiency of FPGA CPU usage compared to ARM processors is 14.89\%.

\subsection{Memory Usage}

@@

Memory usage with ARM processors and FPGA can be seen in the \ ref{table:mem-results} table and the chart in the \ref{fig:chart-mem} image. This data shows the percentage memory used in each kernel. The average usage of memory with an ARM processor is 25.37\% and 24.86\% with an FPGA.

\begin{atable}
    \caption{Comparison table of Memory Usage using ARM prosesor and FPGA.}
    \label{table:hasil-mem}
    \csvreader[
        head to column names,
        tabular=lcc,
        separator=semicolon,
        before table=\rowcolors{2}{gray!15}{gray!30},
        table head= \rowcolor{gray!50!black} 
            \color{white} Filter & 
            \color{white} Prosesor ARM (\%) & 
            \color{white} FPGA (\%)\\]
        {tables/hasil-mem.csv}
        {
            filter=\filter, 
            arm=\arm, 
            fpga=\fpga}
        {
            \filter & 
            \arm & 
            \fpga }
\end{atable}

\begin{figure}[H]
    \includegraphics[width=0.81\linewidth, center]{images/chart/chart-mem.png}
    \caption{Comparison chart of Memory Usage using ARM prosesor and FPGA.}
    \label{fig:chart-mem}
\end{figure}

@@

    \item Compute time with FPGA 88.85\% better than ARM processor. The filtered video with the ARM processor gets an average of 6.95 fps while the FPGA average is 60.37 fps. FPS with FPGA is 88.49\% better than ARM processor. CPU usage on FPGA is 14.89\% better, usage of memory on FPGA is 2.02\% better, usage of resident memory is 2.07\% better, and usage of shared memory is 4.08\% better compared to ARM processors. Meanwhile, the use of virtual memory on ARM processors is 0.03\% better than FPGA.
\end{enumerate}

>>>>

\subsection{Convolution}

@@

The researchers used computation time, frame rate (FPS), CPU loads, memory usage, resident memory (RES), shared memory (SHR), and virtual memory usage (VIRT) to measure the performance of applying linear spatial filters with ARM and FPGA processors.

@@

\subsubsection{CPU Loads}
% Pada penelitian ini peneliti menggunakan fitur yang tersedia pada sistem operasi Linux yang berjalan di FPGA Development Board untuk melihat persentase penggunaan CPU pada proses penerapan filter spasial linear. Program ini menampilkan informasi tentang proses-proses yang berjalan pada sistem operasi seperti ID sebuah proses, user yang menjalankan proses tersebut, \textit{memory} yang digunakan, status sebuah proses, persentase CPU yang digunakan dan lainnya.

The researchers used the features available on the Linux operating system running on the FPGA Development Board to see the percentage of CPU loads in the process of applying linear spatial filters. This program displays information about processes running on the operating system such as the ID of a process, the user running the process, the memory used, the status of a process, the percentage of CPU used and others.

\subsubsection{Memory Utilize}

@@

\subsection{System Design}
\begin{figure}[ht]
    \includegraphics[width=1\linewidth, center]{images/rancangan-sistem2.png}
    \caption{System Design.}
    \label{fig:rancangan-sistem}
\end{figure}

@@

The spatial filter process is carried out by convolution operations on each matrix with a predetermined kernel. This convolutional operation produces a new matrix 1280x720. The resulting matrix is then represented as a digital image, hereinafter referred to as the filter result. The filter result of each frame is displayed to the monitor via HDMI Output on the FPGA Development Board continuously.

@@

% Data waktu komputasi menggunakan 200 frame pada maasing-masing kernel dapat dilihat pada tabel \ref{table:hasil-time200} dan grafik pada gambar \ref{fig:chart-time200}. Rata-rata waktu komputasi dengan prosesor ARM menggunakan 200 frame adalah 29,06 detik, sedangkan rata-rata waktu komputasi dengan FPGA menggunakan 200 frame hanya 3,32 detik.

@@

\subsection{CPU Loads}

@@

Comparative data on CPU loads on each kernel with ARM and FPGA processors can be seen in the \ref{table:cpu-result} table and the chart in the \ref{fig:chart-cpu} table. The average CPU loads with ARM processors is 99.58\% while with FPGA it is 84.75\%. This data shows that CPU loads with ARM processors is slightly greater than with FPGAs.

\begin{atable}
    \caption{Comparison table of cpu usage using ARM prosesor and FPGA.}
    \label{table:hasil-cpu}
    \csvreader[
        head to column names,
        tabular=lcc,
        separator=semicolon,
        before table=\rowcolors{2}{gray!15}{gray!30},
        table head= \rowcolor{gray!50!black} 
            \color{white} Filter & 
            \color{white} Prosesor ARM (\%) & 
            \color{white} FPGA (\%)\\]
        {tables/hasil-cpu.csv}
        {
            filter=\filter, 
            arm=\arm, 
            fpga=\fpga}
        {
            \filter & 
            \arm & 
            \fpga }
\end{atable}
\begin{figure}[H]
    \includegraphics[width=0.81\linewidth, center]{images/chart/chart-cpu.png}
    \caption{Comparison chart of CPU loads using ARM prosesor and FPGA.}
    \label{fig:chart-cpu}
\end{figure}

@@

The biggest CPU loads with ARM processors is the average blur kernel (99.83\%) and the FPGA on the sobel horizontal kernel (86.22\%). The CPU loads with ARM processors is the sharpening and sobel horizontal kernel (99.47\%) and with the FPGA on the gaussian blur kernel (83.70\%).

@@

To calculate the CPU loads efficiency of an FPGA compared to an ARM processor, the following equation is used:
\begin{equation*}
    % \label{eq:efisiensi}
    \begin{split}
& = 100\% - \left( \frac{CPU\ FPGA}{CPU\ ARM Prosesor} \times 100\% \right) \\
& = 100\% - \left( \frac{84.75}{99.58} \times 100\% \right) \\
& = 100\% - 85.11\% \\
& = 14.89\% \\
    \end{split}
\end{equation*}
% sehingga diperoleh efisiensi penggunaan CPU FPGA dibandingkan dengan prosesor ARM adalah sebesar 14.89\%.

the efficiency of FPGA CPU loads compared to ARM processors is 14.89\%.

\subsection{Memory Utilize}

@@

Memory utilize with ARM processors and FPGA can be seen in the \ ref{table:mem-results} table and the chart in the \ref{fig:chart-mem} image. This data shows the percentage memory used in each kernel. The average usage of memory with an ARM processor is 25.37\% and 24.86\% with an FPGA.

\begin{atable}
    \caption{Comparison table of Memory Utilize using ARM prosesor and FPGA.}
    \label{table:hasil-mem}
    \csvreader[
        head to column names,
        tabular=lcc,
        separator=semicolon,
        before table=\rowcolors{2}{gray!15}{gray!30},
        table head= \rowcolor{gray!50!black} 
            \color{white} Filter & 
            \color{white} Prosesor ARM (\%) & 
            \color{white} FPGA (\%)\\]
        {tables/hasil-mem.csv}
        {
            filter=\filter, 
            arm=\arm, 
            fpga=\fpga}
        {
            \filter & 
            \arm & 
            \fpga }
\end{atable}

\begin{figure}[H]
    \includegraphics[width=0.81\linewidth, center]{images/chart/chart-mem.png}
    \caption{Comparison chart of Memory Utilize using ARM prosesor and FPGA.}
    \label{fig:chart-mem}
\end{figure}

@@

    \item Compute time with FPGA 88.85\% better than ARM processor. The filtered video with the ARM processor gets an average of 6.95 fps while the FPGA average is 60.37 fps. FPS with FPGA is 88.49\% better than ARM processor. CPU loads on FPGA is 14.89\% better, usage of memory on FPGA is 2.02\% better, usage of resident memory is 2.07\% better, and usage of shared memory is 4.08\% better compared to ARM processors. Meanwhile, the use of virtual memory on ARM processors is 0.03\% better than FPGA.
\end{enumerate}
